---
title: "CTU quarterly report `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      warning = FALSE, 
                      message = FALSE,
                      echo = FALSE)
library(pf)
library(tidyverse)
```

```{r, include=FALSE}
all_tabs <- getPFData()
```



```{r dataprep, echo=FALSE}
y <- prepTime(all_tabs) %>% 
  mutate(money = billable_time / 60 * UNITPRICE) %>% 
  left_join(all_tabs$project %>% select(cf_applicable_ordinance_2, PK_Project),
            by = c("top_project" = "PK_Project")) %>% 
  mutate(ordinance = str_replace(cf_applicable_ordinance_2, "If ", ""),
         ordinance = str_replace(ordinance, "/.{1,}$", "")) %>% 
  group_by(ctu_projectName, projnum, ctu_division, projecttype, year, q_in_year, billable, ordinance) %>% 
  summarize(across(c(billable_time, nonbillable_time, money), sum, na.rm = TRUE),
            ) %>% 
  mutate(across(ends_with("time"), ~ .x / 60)) %>% 
  filter(year > 2019) %>% 
  left_join(projectSize(all_tabs)) %>%
  mutate(quarter = year + ((1/4 * q_in_year) - 0.25)) %>% 
  ungroup() %>% 
  mutate(ordinance = ifelse(!is.na(ordinance), ordinance, "unknown"))

z <- y %>% 
  group_by(ctu_division, projecttype, year, q_in_year, quarter, billable, ordinance, size) %>% 
  summarize(across(c(billable_time, nonbillable_time, money), sum, na.rm = TRUE),
            n = nrow(.data))

```
### Money
#### Money by ordinance

```{r}
z  %>% 
  ggplot(aes(x = quarter, y = money, fill = ctu_division, alpha = ordinance)) +
  geom_col() +
  coord_flip() +
  scale_alpha_manual(values = c(1, .8, .6, .4)) +
  guides(alpha = guide_legend(title = "Ordinance", nrow = 2, byrow = TRUE, reverse = TRUE),
         fill = guide_legend(title = "Division", nrow = 1, byrow = TRUE, reverse = TRUE)) +
  theme(panel.background = element_rect(fill = NA),
        legend.position = "bottom", 
        legend.box = "vertical")

```

#### Money by project size

```{r}
z  %>% 
  ggplot(aes(x = quarter, y = money, fill = ctu_division, alpha = size)) +
  geom_col() +
  coord_flip() +
  scale_alpha_manual(values = c(1, .8, .6)) +
  guides(alpha = guide_legend(title = "Size", nrow = 1, byrow = TRUE, reverse = TRUE),
         fill = guide_legend(title = "Division", nrow = 1, byrow = TRUE, reverse = TRUE)) +
  theme(panel.background = element_rect(fill = NA),
        legend.position = "bottom", 
        legend.box = "vertical")
```

### Billable time
#### Billable time by ordinance

```{r}
z  %>% 
  ggplot(aes(x = quarter, y = billable_time, fill = ctu_division, alpha = ordinance)) +
  geom_col() +
  coord_flip() +
  scale_alpha_manual(values = c(1, .8, .6, .4)) +
  guides(alpha = guide_legend(title = "Ordinance", nrow = 2, byrow = TRUE, reverse = TRUE),
         fill = guide_legend(title = "Division", nrow = 1, byrow = TRUE, reverse = TRUE)) +
  theme(panel.background = element_rect(fill = NA),
        legend.position = "bottom", 
        legend.box = "vertical")

```

#### Billable time by project size

```{r}
z  %>% 
  ggplot(aes(x = quarter, y = billable_time, fill = ctu_division, alpha = size)) +
  geom_col() +
  coord_flip() +
  scale_alpha_manual(values = c(1, .8, .6)) +
  guides(alpha = guide_legend(title = "Size", nrow = 1, byrow = TRUE, reverse = TRUE),
         fill = guide_legend(title = "Division", nrow = 1, byrow = TRUE, reverse = TRUE)) +
  theme(panel.background = element_rect(fill = NA),
        legend.position = "bottom", 
        legend.box = "vertical")
```

### Non-Billable time

(includes consultings)

#### Non-Billable time by ordinance

```{r}
z  %>% 
  ggplot(aes(x = quarter, y = nonbillable_time, fill = ctu_division, alpha = ordinance)) +
  geom_col() +
  coord_flip() +
  scale_alpha_manual(values = c(1, .8, .6, .4)) +
  guides(alpha = guide_legend(title = "Ordinance", nrow = 2, byrow = TRUE, reverse = TRUE),
         fill = guide_legend(title = "Division", nrow = 1, byrow = TRUE, reverse = TRUE)) +
  theme(panel.background = element_rect(fill = NA),
        legend.position = "bottom", 
        legend.box = "vertical")

```

#### Non-Billable time by project size

```{r}
z  %>% 
  ggplot(aes(x = quarter, y = nonbillable_time, fill = ctu_division, alpha = size)) +
  geom_col() +
  coord_flip() +
  scale_alpha_manual(values = c(1, .8, .6)) +
  guides(alpha = guide_legend(title = "Size", nrow = 1, byrow = TRUE, reverse = TRUE),
         fill = guide_legend(title = "Division", nrow = 1, byrow = TRUE, reverse = TRUE)) +
  theme(panel.background = element_rect(fill = NA),
        legend.position = "bottom", 
        legend.box = "vertical")
```


#### To explore for yourself...

##### Aggregated to division, project type, quarter in year, billable (Y/N), ordinance, and size

```{r}
DT::datatable(z, filter = "top")
```


##### Aggregated to project, division, project type, quarter in year, billable (Y/N), ordinance, and size

```{r}
DT::datatable(y, filter = "top")
```





Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
